### 2021-06-09 figures/results/tables/student_infections_table.tex
New results figures and tables with both shapley decompositions.

\begin{tabular}{lr}
\toprule
{} &  predicted total infections among 5-14 year olds from Easter until 2021-05-31 \\
scenario                               &                                                                               \\
\midrule
 educ open after easter  without tests &                                             752932 \\
 educ open after easter  with tests    &                                             583570 \\
 close educ after easter               &                                             443978 \\
 baseline                              &                                             459436 \\
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{lr}
\toprule
{} &  predicted total infections among 5-14 year olds from Easter until 2021-05-31 \\
scenario                               &                                                                               \\
\midrule
 educ open after easter  without tests &                                             775324 \\
 educ open after easter  with tests    &                                             604078 \\
 close educ after easter               &                                             469274 \\
 baseline                              &                                             478080 \\
\bottomrule
\end{tabular}
